Calendar-based graphics for visualizing people's daily schedules

### 2019-02-19 reviews/response.Rmd

---
title: Response to reviewers
author: JCGS-18-293
output:
  MonashEBSTemplates::memo:
    includes:
      in_header: preamble2.tex
fontfamily: mathpazo
---

Thanks to the three reviewers for some very helpful comments which have led to many improvements of the paper. My response are in black, the reviewers' comments are in red.

# Reviewer 1 comments

### 2019-02-21 reviews/response.Rmd

---
title: Response to reviewers
author: JCGS-18-293
output:
  MonashEBSTemplates::memo:
    includes:
      in_header: preamble2.tex
fontfamily: mathpazo
---

Thanks to the three reviewers for some very helpful comments which have led to many improvements of the paper. My response are in black, the reviewers' comments are in red.

# Reviewer 1 comments

# Reviewer 2 comments

> p.10, l.1-15 It wasn't clear to me why the subtraction was performed in the equation (2) because I couldn't find any description for the global coordinate system of the canvas. The value of y could be negative. Please add the description how to deal with the coordinate system, especially the y-axis.

The reason why the subtraction is performed was given in the following paragraph of Equation (2).

### 2019-02-21 main.Rmd
uploaded reviews
chinese embedded using showtext

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE, 
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = FALSE, external = TRUE, dev = "pdf",
  fig.height = 5, fig.width = 8, out.width = "\\textwidth"
)
read_chunk('src/main.R')
```

@@

```{r chn-embedded, fig.cap = "The same plot as Figure \\ref{fig:boxplot}, but with the month and week day labels in Chinese. It demonstrates the natural support for languages other than English."}
include_graphics("img/chn-1-embedded.pdf")
```

@@

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE, 
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = TRUE, external = TRUE, dev = "pdf",
  fig.height = 5, fig.width = 8, out.width = "\\textwidth"
)
read_chunk('src/main.R')
```

@@

```{r chn}
```

```{r chn-embedded, fig.cap = "The same plot as Figure \\ref{fig:boxplot}, but with the month and week day labels in Chinese. It demonstrates the natural support for languages other than English."}
include_graphics("figure/chn-1.pdf")
```

@@

## Reasons to use calendar-based displays
